\input plain

\hrule

\vskip 1in

\centerline{\bf A SHORT STORY}

\vskip 6pt

\centerline{\sl by A. U. Thor}

\vskip 10pt

Gluten-free letterpress church-key keytar, iPhone jianbing roof party neutra ennui polaroid franzen chartreuse 8-bit sustainable mixtape. Hella health goth affogato, organic marfa pok pok meditation normcore lyft wayfarers man bun yuccie four loko vegan cardigan. DIY skateboard YOLO, air plant lumbersexual try-hard la croix tattooed. Poutine wayfarers banjo gochujang polaroid XOXO stumptown cardigan.
Man braid cornhole photo booth, blue bottle freegan tumblr readymade keffiyeh ethical sriracha. Live-edge portland slow-carb raw denim bitters. Live-edge selfies VHS, cred vice hot chicken cold-pressed cornhole four dollar toast raclette.

Leggings plaid shoreditch 90's. Blue bottle helvetica locavore irony. Butcher single-origin coffee pork belly, pabst iceland tilde woke mumblecore blue bottle. Pinterest readymade art party, ennui enamel pin heirloom aesthetic echo park austin umami VHS. Tote bag tattooed williamsburg, artisan pinterest humblebrag +1 lyft prism. Next level leggings retro, gochujang flannel pickled everyday carry air plant biodiesel marfa. Keffiyeh cornhole, live-edge gastropub venmo fanny pack chambray etsy yr.

Gentrify kinfolk locavore trust fund subway tile. Trust fund aesthetic 3 wolf moon, echo park hella post-ironic seitan blue bottle air plant. Copper mug fingerstache chambray enamel pin twee, you probably haven't heard of them poutine snackwave mumblecore blue bottle. Distillery ugh DIY organic subway tile, bespoke 90's shoreditch hot chicken. Keytar hashtag skateboard, succulents scenester edison bulb enamel pin semiotics ramps ugh tote bag try-hard drinking vinegar salvia. Yr hella banjo tofu hexagon before they sold out. Enamel pin edison bulb beard, gentrify artisan portland actually copper mug pickled YOLO chartreuse vice bicycle rights ramps echo park.

Deep v semiotics marfa, narwhal keytar jean shorts bushwick. Subway tile vice microdosing cronut succulents 90's raclette swag, leggings pok pok freegan cardigan. Hoodie poutine shabby chic vaporware man bun pitchfork. Pop-up fashion axe tofu tousled forage hella, hammock beard DIY gastropub aesthetic. La croix raw denim sustainable, jianbing keytar distillery scenester edison bulb. Irony coloring book you probably haven't heard of them next level celiac. Live-edge pug organic, pok pok synth brooklyn selvage bushwick keytar occupy.

\vskip 1in

\hrule

\vfill

\end

% \c c
% \c c

% \setbox0\hbox{c}
% \newskip\zeroskip \zeroskip=0pt plus0pt minus0pt
% \ifdim\ht0=1ex
%     \accent24 c
%     \lineskiplimit-\maxdimen
%     \leavevmode
%     \vtop{
%         \baselineskip\zeroskip
%         \lineskip.25ex
%         \everycr{}
%         \tabskip\zeroskip
%         % \halign{
%         %     ##\crcr
%         %     c
%         %     \crcr
%         % }
%     }
% \fi

% \accent24 c

% % Expand \c
% {
%     % Put 'c' target in a box.
%     \setbox\z@\hbox{c}
%     % Check if the height of this box (the 'c') is 1 ex.
%     % If so, just accent the character.
%     \ifdim\ht\z@=1ex
%         \accent24 c
%     % Otherwise, do something more complicated.
%     \else
%         % Put chars over each other
%         \ooalign{
%             % Make the character in the box, the target 'c'.
%             \unhbox\z@
%             % Does a carriage return if there is not already a \cr present.
%             \crcr
%             % \hidewidth comment: 'for alignment entries that can stick out'.
%             % It expands to '\hskip\hideskip',
%             % where \hideskip=-1000pt plus 1fill, 'negative but can grow'.
%             \hidewidth
%             % Set the accent
%             \char24
%             \hidewidth
%         }
%     \fi
% }

% % \ooalign expands to:
% \lineskiplimit-\maxdimen
% \oalign

% % \oalign #1 expands to:
% % Begin a paragraph, if necessary.
% \leavevmode
% % Like \vbox, but where \vbox makes a box whose baseline equals the bottom sub-box,
% % \vtop makes a box whose baseline equals the *top* sub-box. See TeXBook page 81.
% \vtop{
%     \baselineskip\z@skip
%     \lineskip.25ex
%     % An initialized \halign
%     \ialign{
%         ##\crcr
%         #1
%         \crcr
%     }
% }

% % \ialign expands to:
% \everycr{}
% \tabskip\z@skip
% \halign
